A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-08-20 main.tex

\begin{figure*}
    \centering
    \includegraphics[width=.8\textwidth]{plots/architecture.pdf}
    \caption{Cloud Architecture Diagram}
    \label{fig:architecture}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=.6\textwidth]{plots/architecture.pdf}
    \caption{For our experiments we used 5 concurrent nodes. The left column depicts each node used for monitoring the experiments running on the others-- one for each tested GPU. The power, performance, and timing metrics, were then stored on  persistent volume claim (PVC) is a request for storage by a user. Object storage is...
    1000 trials were run for each dataset and hardware device.}
    \label{fig:architecture}
\end{figure*}
